Contextuality and the Born rule in fuzzy quantum theories

### 2017-03-17 prop_letter.tex
prop_letter.tex Give up bibLaTeX, roll back to bibTeX...
prop_letter.tex Updating...

\documentclass[reprint, aps, prl,superscriptaddress, showpacs,
showkeys]{revtex4-1} 
% Follow 
% https://tex.stackexchange.com/questions/37076/is-it-possible-to-load-biblatex-with-a-class-that-has-already-loaded-natbib/37077#37077
% to put RevTeX with BibLaTeX
\let\bibhang\relax
\let\citename\relax
\let\bibfont\relax
\let\Citeauthor\relax
\let\textcite\relax
\makeatletter
\DeclareRobustCommand{\MakeUppercase}[1]{{%
      \def\i{I}\def\j{J}%
      \def\reserved@a##1##2{\let##1##2\reserved@a}%
      \expandafter\reserved@a\@uclclist\reserved@b{\reserved@b\@gobble}%
      \protected@edef\reserved@a{\uppercase{#1}}%
      \reserved@a
   }}
\DeclareRobustCommand{\MakeLowercase}[1]{{%
      \def\reserved@a##1##2{\let##2##1\reserved@a}%
      \expandafter\reserved@a\@uclclist\reserved@b{\reserved@b\@gobble}%
      \protected@edef\reserved@a{\lowercase{#1}}%
      \reserved@a
   }}
\makeatother
\expandafter\let\csname ver@natbib.sty\endcsname\relax
\usepackage[ backend=biber,style=phys,%
articletitle=false,biblabel=brackets,%
chaptertitle=false,pageranges=false%
]{biblatex}
\addbibresource{prop.bib}
\ExecuteBibliographyOptions{sorting=none,doi=false,isbn=false,url=false}
\usepackage{fullpage}
\usepackage[T1,T2A]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{bbold}
\usepackage{wesa}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{hyperref}

@@

\begin{document}
\renewcommand{\bibliography}[1]{}

@@

\begin{abstract}
\begin{description}
\item[Background] In a world of bounded resource, any quantum measurement can
be only performed in finite precision.
\item[Method] We model idea of the finite precision measurement as finite number
of intervals, and the replace quantum real-valued probability measures by
interval-valued ones.
\item[Results] Quantum interval-valued probability measures provide a unified
framework to interpret the Kochen-Specker theorem and Gleason's theorem as
two limit cases. For the cases between them, we found some legitimate quantum
interval-valued probability measures which cannot be explained by the Born rule.
While restricting to only commuting projectors, the interval-valued probability
measures become classical, and these non-Born interval-valued probability
measures disappear.
\item[Conclusions] Our research provides a new insight of finite precision
measurement and non-commutativity when formulating quantum theory.
\end{description}
\end{abstract}

@@

The
Kochen-Specker theorem asserts that there is no function~$v$ assigning
a definitely value to all observables such that
\begin{eqnarray}
& & v\left(O_{1}\right)+v\left(O_{2}\right)=v\left(O_{1}+O_{2}\right)\textrm{ and}\\
& & v\left(O_{1}\right)v\left(O_{2}\right)=v\left(O_{1}O_{2}\right)
\label{eq:Kochen-Specker-Rules}\end{eqnarray}
if $O_{1}$ and $O_{2}$ are commuting observables. Suppose that there
is a function~$v$ satisfying these two properties, it must send
an observable to its eigenvalues so that the following observables~\cite{Mermin1990Simple,peres1995quantum}:
\begin{equation}
\begin{array}{ccc}
\mathbb{1}\otimes\sigma_{z} & \sigma_{z}\otimes\mathbb{1} & \sigma_{z}\otimes\sigma_{z}\\
\sigma_{x}\otimes\mathbb{1} & \mathbb{1}\otimes\sigma_{x} & \sigma_{x}\otimes\sigma_{x}\\
\sigma_{x}\otimes\sigma_{z} & \sigma_{z}\otimes\sigma_{x} & \sigma_{y}\otimes\sigma_{y}
\end{array}\label{eq:MerminSquare}
\end{equation}
must be sent to $1$ or $-1$. In each row and column, operators commutes,
and each operator is the product of the two others, except in the
third column $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
Therefore, it is clear impossible to find a function~$v$ such that
\begin{equation}
\begin{array}{ccc}
v\left(\mathbb{1}\otimes\sigma_{z}\right) & v\left(\sigma_{z}\otimes\mathbb{1}\right) & v\left(\sigma_{z}\otimes\sigma_{z}\right)\\
v\left(\sigma_{x}\otimes\mathbb{1}\right) & v\left(\mathbb{1}\otimes\sigma_{x}\right) & v\left(\sigma_{x}\otimes\sigma_{x}\right)\\
v\left(\sigma_{x}\otimes\sigma_{z}\right) & v\left(\sigma_{z}\otimes\sigma_{x}\right) & v\left(\sigma_{y}\otimes\sigma_{y}\right)
\end{array}\label{eq:MerminSquare-values}
\end{equation}
satisfying equation~(\ref{eq:Kochen-Specker-Rules}).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{comment}
 \bibliographystyle{plain}
\bibliography{prop}
\end{comment}
\printbibliography

>>>>

\documentclass[reprint, aps, prl,superscriptaddress, showpacs,
showkeys]{revtex4-1} 
\usepackage{fullpage}
\usepackage[T1,T2A]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{bbold}
\usepackage{wesa}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{hyperref}

@@

\begin{document}

@@

\begin{abstract}
~
\begin{description}
\item [{Background}] In a world of bounded resource, any quantum measurement
can be only performed in finite precision. {\small \par}
\item [{Method}] We model idea of the finite precision measurement as finite
number of intervals, and replace quantum real-valued probability measures
by interval-valued ones. {\small \par}
\item [{Results}] Quantum interval-valued probability measures provide
a unified framework to interpret the Kochen-Specker theorem and Gleason's
theorem as two limit cases. For the cases between them, we found some
legitimate quantum interval-valued probability measures which cannot
be explained by the Born rule. While restricting on only commuting
projectors, the interval-valued probability measures become classical,
and these non-Born interval-valued probability measures disappear. {\small \par}
\item [{Conclusions}] Our research provides a new insight of finite precision
measurement and non-commutativity when formulating quantum theory. {\small \par}
\end{description}
\end{abstract}

@@

Textbook quantum mechanics asserts that the probability of a measurement
can be computed from wave function of the system and the measuring
observable \emph{exactly}.

The Kochen-Specker theorem asserts that there is no function~$v$
assigning a definitely value to all observables such that 
\begin{eqnarray}
 &  & v\left(O_{1}\right)+v\left(O_{2}\right)=v\left(O_{1}+O_{2}\right)\textrm{ and}\\
 &  & v\left(O_{1}\right)v\left(O_{2}\right)=v\left(O_{1}O_{2}\right)\label{eq:Kochen-Specker-Rules}
\end{eqnarray}
if $O_{1}$ and $O_{2}$ are commuting observables. Suppose that there
is a function~$v$ satisfying these two properties, it must send
an observable to its eigenvalues so that the following observables~\citep{Mermin1990Simple,peres1995quantum}:
\begin{equation}
\begin{array}{ccc}
\mathbb{1}\otimes\sigma_{z} & \sigma_{z}\otimes\mathbb{1} & \sigma_{z}\otimes\sigma_{z}\\
\sigma_{x}\otimes\mathbb{1} & \mathbb{1}\otimes\sigma_{x} & \sigma_{x}\otimes\sigma_{x}\\
\sigma_{x}\otimes\sigma_{z} & \sigma_{z}\otimes\sigma_{x} & \sigma_{y}\otimes\sigma_{y}
\end{array}\label{eq:MerminSquare}
\end{equation}
must be sent to $1$ or $-1$. In each row and column, operators commutes,
and each operator is the product of the two others, except in the
third column $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
Therefore, it is clear impossible to find a function~$v$ such that
\begin{equation}
\begin{array}{ccc}
v\left(\mathbb{1}\otimes\sigma_{z}\right) & v\left(\sigma_{z}\otimes\mathbb{1}\right) & v\left(\sigma_{z}\otimes\sigma_{z}\right)\\
v\left(\sigma_{x}\otimes\mathbb{1}\right) & v\left(\mathbb{1}\otimes\sigma_{x}\right) & v\left(\sigma_{x}\otimes\sigma_{x}\right)\\
v\left(\sigma_{x}\otimes\sigma_{z}\right) & v\left(\sigma_{z}\otimes\sigma_{x}\right) & v\left(\sigma_{y}\otimes\sigma_{y}\right)
\end{array}\label{eq:MerminSquare-values}
\end{equation}
satisfying equation~(\ref{eq:Kochen-Specker-Rules}).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliography{prop}
